The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-06 document/ms.tex
words about ors

Combining these detection effects, the total detection efficiency is given by
\begin{eqnarray}
Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
                 Q_{\mathrm{win},k} (\params) \,
                 Q_{\mathrm{geom},k} (\params) \quad.
\end{eqnarray}
\dfmtodo{Talk about doing integrals with this.}

% For the purposes of this \paper, we are not considering the occurrence rate of
% exoplanets as a function of stellar properties; we will only measure an
% average rate across the target sample that we previously selected.
% Therefore, it is sufficient to estimate the marginalized detection efficiency
% integrated with respect to our prior distributions on the nuisance parameters.
% In this case, the only parameters that we will consider are planet radius and
% orbital period.
% Under this model, the relevant detection efficiency function for long-period
% transiting planets is
% \begin{eqnarray}\eqlabel{full-comp}
% Q(R,\,P) &=& \frac{1}{K} \sum_{k=1}^{K} \int Q_k(\params) \,
%     p(\params_{\{R,\,P\}}) \dd\params_{\{R,\,P\}}
% \end{eqnarray}
% where $\params_{\{R,\,P\}}$ indicates the set of all parameters except radius
% and period.

% Since the simulated parameters in the injection and recovery tests described
% above were sampled from the prior distribution $p(\params_{\{R,\,P\}})$, the
% easiest way to estimate \eq{full-comp} is to take the ratio of the weighted
% histogram of the recovered injections to the weighted histogram of all
% simulations where each simulation is weighted by
% $Q_{\mathrm{win},k} (\params) \, Q_{\mathrm{geom},k} (\params)$ evaluated at
% the parameters of the simulation.
% \dfmtodo{Some figure} shows the measured completeness (\eq{full-comp}) as a
% function of planet radius and orbital period.

% \dfmtodo{Analytic fit?}

@@

Assuming a Poisson likelihood, the occurrence rate density in a volume
$V$~--~defined as $P_\mathrm{min} \le P < P_\mathrm{max}$ and
$R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
\begin{eqnarray}\eqlabel{rate-density}
\Gamma_V \equiv \frac{\dd N}{\dd\ln P\dd\ln R} &=&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\end{eqnarray}
where $N$ is the expected number of planets per G/K dwarf, $C(\cdots)$ is the
number of planets in the volume, and
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
    \sum_{k=1}^{K} \int p(w_{P,\,R})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
\end{eqnarray}
where $p(w_{P,\,R})$ is the prior distribution of all the parameters except
the period and radius.
Using the $J$ injections sampled uniformly in period and radius and other
parameters from $p(w_{P,\,R})$,
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
\end{eqnarray}
where the sum is over all injections in the volume $V$.

>>>>

Combining these detection effects, the total detection efficiency is given by
\begin{eqnarray}
Q_k(\params) &=& Q_{\mathrm{det},k}(\params) \,
                 Q_{\mathrm{win},k} (\params) \,
                 Q_{\mathrm{geom},k} (\params) \quad.
\end{eqnarray}

@@

Assuming a Poisson likelihood, the occurrence rate density in a volume
$V$~--~defined as $P_\mathrm{min} \le P < P_\mathrm{max}$ and
$R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
\citep[see, for example, the Appendix of][]{Foreman-Mackey:2014}
\begin{eqnarray}\eqlabel{rate-density}
\Gamma_V \equiv \frac{\dd N}{\dd\ln P\dd\ln R} &=&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\end{eqnarray}
where $N$ is the expected number of planets per G/K dwarf, $C(\cdots)$ is the
number of planets in the volume, and
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
    \sum_{k=1}^{K} \int p(w_{\{P,\,R\}})\,Q_k(w)\,\bvec{1}[P,\,R\in V]\dd w
\end{eqnarray}
where $p(w_{\{P,\,R\}})$ is the prior distribution of all the parameters except
the period and radius and $\bvec{1}[\cdot]$ is 1 if the argument is satisfied
and 0 otherwise.
Using the $J$ injections sampled uniformly in period and radius and other
parameters from $p(w_{\{P,\,R\}})$,
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
\end{eqnarray}
where the sum is over all injections in the volume $V$.
